The History of Social Work Research: A Data Science Perspective

### 2015-01-29 Analysis.Rmd
Processed wrangled R object.

# Wrangle the data with the BWR function suite
ebscoBWR.f(csv=FALSE, path=path)
#save(bwr.df, file = "piArticles.R")
```

>>>>

# Wrangle the data with the BWR function suite
start.time <- Sys.time()
ebscoBWR.f(csv=FALSE, path=path)
end.time <- Sys.time()
end.time-start.time
#save(bwr.df, file = "HistoricalArticles.R")
```
